Practicing with Survival Analysis

### 2017-07-11 practice_survivalanalysis.Rmd
minor changes

#creating survival object
surv_object <- Surv(out1$time_until_answer, out1$answered)
```

@@

#cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability")
#lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
#lines(cb$time, cb$upper, lty=3, type="s")

#estimate means survival time E(T)
#estimate percentiles of survival time
```

### instantaneous hazard using epiR package
```{r}
library(epiR)
h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s")
plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1500000), type = "s")

```

@@

#plotting both KM and Nelson Aalen on same graph
plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s")
points(c(fit$time, 6500000), H.tilde, lty=2, type="s")
legend("topleft", legend=c("H.hat","H.tilde"), lty=1:2)
#KM and Nelson Aalen estimators look the same- because large data set? 
```

### mean, medians, percentiles 
```{r}
#at 30,158 seconds (502.6 min), 50% of the questions have been answered
#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
#upper limit = largest observation in time to event var
print(KM.obj, print.rmean=TRUE)

>>>>

#creating survival object
surv_object <- Surv(out1$time_until_answer, out1$answered, type = "right")
```

@@

#cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability")
#lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
#lines(cb$time, cb$upper, lty=3, type="s")
```

### instantaneous hazard using epiR package
```{r}
library(epiR)
h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s")
plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s")
#there is a spike in instantaneous hazard before 200,000 seconds (55.5 hours or 2.31 days)
```

@@

#plotting both KM and Nelson Aalen on same graph
plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s")
points(c(fit$time, 6500000), H.tilde, lty=2, type="s")
legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
#KM and Nelson Aalen estimators look the same- because large data set? 
#Rate of increase in cumulative hazard spikes up drastically (immediately after question is posted)- indicating that hazard is increasing on that interval. Rate of increase in cumulative hazard after a certain point, levels out pretty quickly- indicating that hazard is decreasing
```

### mean, medians, percentiles 
```{r}
#at 30,158 seconds (502.6 min, 8.38 hours), 50% of the questions have been answered
#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
#upper limit = largest observation in time to event var
print(KM.obj, print.rmean=TRUE)
